Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Add an answer for @kazu

\begin{quote}
    \emph{kazu: Monoid is already described in Introduction. Why is this repeated? And ``code documentation'' is aslo already dicussed in Introduction. I think we can use ``code documentation'' here.}
\end{quote}

>>>>

\begin{quote}
    kazu: Monoid is already described in Introduction. Why is this
    repeated? And ``code documentation'' is aslo already dicussed in
    Introduction. I think we can use ``code documentation'' here.

    sol: We reuse Monoid here, but we make a different point.  So this
    still adds something, and I think we need it.
\end{quote}
